Review: Adaptive Introgression Expanded the Genetic Base of Crops during post-Domestication Spread

### 2017-07-07 paper.tex

\begin{figure}[h]
	\centering
	\includegraphics[width=17.35cm]{par_figure_stars.png}
	\caption{Map of the natural ranges of wild relatives of four domesticated crops, overlayed with average annual temperature.}
	\label{boxplot:map}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=17.35cm]{boxplot.png}
	\caption{The distribution of average annual temperature experienced in the geographic home ranges of wild relatives interfertile with four crops}
	\label{fig:map}
\end{figure}

@@

\subsection*{What candidate genes were targeted by selection during domestication?}
Loci targeted by selection during domestication can be identified through so-called ``bottom-up'' approaches based on population genetic signatures \cite{Ross-Ibarra2007}.
Ideally, candidate loci will be identified by first constructing a demographic model representing the history of the domesticate.
In this approach, diversity data from neutral loci are fit to potential models of a crop's demography and then statistical tests of selection are used to identify candidate domestication genes under the most likely model.
Due to the difficulty of this approach and the uncertainty associated with any given demography, many studies identify domestication loci using a strict outlier approach in which loci showing the greatest reduction in nucleotide diversity or the highest allele frequency differentiation in the domesticate relative to the wild progenitor are identified as candidates.
Introgression during crop expansion may influence candidate gene detection using both demographic-modeling and strict-outlier approaches.
For example, \emph{mexicana} introgression into maize described above accounts for approximately 20\% of the genome of maize in the highlands of Mexico \cite{vanHeerwaarden2011}.
Takuno and co-authors \cite{Takuno2015} have shown that a demographic model incorporating this introgression is a significantly better fit to empirical data than a model lacking introgression.
Failure to account for introgression in maize would therefore compromise domestication candidate detection, particularly if a study contained maize samples from the Mexican highlands.
Likewise, introgression that increased nucleotide diversity in the domesticate or decreased differentiation at domestication loci would confound a strict outlier approach.
However, previous work, also in maize, has shown that known domestication loci are particularly resistant to introgression \cite{hufford2013genomic}, likely due to ongoing selection favoring the domesticated phenotype.
\gmj{This is true in most cases I think, although I remember reading that an opposite pattern was found in sunflowers.  I'll go find that paper again and see if it warrants a mention here.}

>>>>

\begin{figure}[h]
	\centering
	\includegraphics[width=17.35cm]{vertical.png}
	\caption{Map of the natural ranges of wild relatives of four domesticated crops, overlayed with average annual temperature.}
	\label{boxplot:map}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=17.35cm]{boxplot_3.png}
	\caption{The distribution of average annual temperature experienced in the geographic home ranges of wild relatives interfertile with four crops}
	\label{fig:map}
\end{figure}

@@

\subsection*{What candidate genes were targeted by selection during domestication?}
Loci targeted by selection during domestication can be identified through so-called ``bottom-up'' approaches based on population genetic signatures \cite{Ross-Ibarra2007}.
Ideally, candidate loci will be identified by first constructing a demographic model representing the history of the domesticate.
In this approach, diversity data from neutral loci are fit to potential models of a crop's demography and then statistical tests of selection are used to identify candidate domestication genes under the most likely model.
Due to the difficulty of this approach and the uncertainty associated with any given demography, many studies identify domestication loci using a strict outlier approach in which loci showing the greatest reduction in nucleotide diversity or the highest allele frequency differentiation in the domesticate relative to the wild progenitor are identified as candidates.
Introgression during crop expansion may influence candidate gene detection using both demographic-modeling and strict-outlier approaches.
For example, \emph{mexicana} introgression into maize described above accounts for approximately 20\% of the genome of maize in the highlands of Mexico \cite{vanHeerwaarden2011}.
Takuno and co-authors \cite{Takuno2015} have shown that a demographic model incorporating this introgression is a significantly better fit to empirical data than a model lacking introgression.
Failure to account for introgression in maize would therefore compromise domestication candidate detection, particularly if a study contained maize samples from the Mexican highlands.
Likewise, introgression that increased nucleotide diversity in the domesticate or decreased differentiation at domestication loci would confound a strict outlier approach.
However, previous work, also in maize, has shown that known domestication loci are particularly resistant to introgression \cite{hufford2013genomic}, likely due to ongoing selection favoring the domesticated phenotype.
\gmj{These expectations do not bear out in sunflower.  The reintroduction of branching in the 70's is likely the cause of this.  Here's the link to the paper: http://onlinelibrary.wiley.com/doi/10.1111/nph.13255/full}
